---
title: "Group 09 CA pollution burden"
author: "Alyssa Kibbe and Halley McVeigh"
date: "11/23/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(janitor)
library(here)
library(hexbin)
```

```{r}
ces <- read.csv(here("data", "ces3demographics.csv")) %>% 
  clean_names()
```


### Basic scatterplot graph % white vs CalEnviroScreen pollution burden score
```{r}
ggplot(data = ces) +
  geom_hex(aes(x = white, y = ces_3_0_score))+
  labs(x = "Whites in Population (%)", y = "CES Score", title = "The Relationship Between CES Score and the Percent White in Population") +
  scale_fill_gradient(low = "navy", high = "orange") +
  theme_minimal()
```

This 2D hexbin plot displays the relationship between % white population of California census tracts versus the corresponding CES (CalEnviroScreen) score. The general trend is one in which communities with a higher % white population have a lower CES score. It is a negative correlation between CES score and % white of a community. 
